### 2014-10-19 PAPER_AMMLY.tex
Change after Levent's feedback

\begin{definition}
The size of the network $\Lambda$ is the total number of network parameters: $\Lambda = \prod_{i=0}^{H-1}n_in_{i+1}$.
\end{definition}

@@

Let $\mathcal{W} = \{w_1,w_2,\dots,w_{\Lambda}\}$ be the set of all weights of the network. Furthermore let $\mathcal{A}_{\Lambda}$ denote the set of all $H$-length configuration of weights chosen from $\mathcal{W}$ (order of weights in a configuration does matter). Note that the size of $\mathcal{A}_{\Lambda}$ is therefore $\Lambda^H$. Also let $\mathcal{B}$ be a set such that each element correspond to the single configuration of weights from Equation~\ref{eq:befrein}, thus $\mathcal{B} = \{(w_{1,1}^1,w_{1,1}^2,\dots,w_{1,1}^H),(w_{1,2}^1,w_{1,2}^2,\dots,w_{1,2}^H),\dots,\\(w_{n_0,\gamma}^1,w_{n_0,\gamma}^2,\dots,w_{n_0,\gamma}^H)\}$, where every single weight comes from set $\mathcal{W}$. Note that in general there might exist elements in $\mathcal{A}_{\Lambda}$ that will never appear in $\mathcal{B}$ and also some elements in $\mathcal{A}_{\Lambda}$ may appear in $\mathcal{B}$ multiple times. Thus Equation~\ref{eq:befrein} can be equivalently written as 
\[Y \!=\! q\!\!\!\!\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!\!\!\left(\sum_{c=1}^{r_{i_1,i_2,\dots,i_H}}\!\!\!X_{i_1,i_2,\dots,i_H}^{(c)}A_{i_1,i_2,\dots,i_H}^{(c)}\!\!\right)\!\!\prod_{k = 1}^{H}w_{i_k},
\]
where $r_{i_1,i_2,\dots,i_H}$ denotes the number of times configuration $(w_{i_1},w_{i_2},\dots,w_{i_H})$ appeared in Equation~\ref{eq:befrein}. Note that $r_{i_1,i_2,\dots,i_H} \in \{\mathbb{Z}^{+}\cup{0}\}$ and furthermore $\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}r_{i_1,i_2,\dots,i_H} = \Psi$. Assuming the independence of $X$'s and $A's$ we get
\[\mathbb{E}_A[Y] = q\!\!\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\left(\sum_{c=1}^{r_{i_1,i_2,\dots,i_H}}X_{i_1,i_2,\dots,i_H}^{(c)}\right)\rho\prod_{k = 1}^{H}w_{i_k}
\]
Let $Y_{\Lambda} = \mathbb{E}_A[Y]$, where in particular $\Lambda$ in this notation refers to the size of set $\mathcal{A}$ (this notation will be helpful later in this section), and define random variables $Z$'s as
\[Z_{i_1,i_2,\dots,i_H=1} = \frac{1}{\sqrt{r_{i_1,i_2,\dots,i_H}}}\sum_{c=1}^{r_{i_1,i_2,\dots,i_H}}X_{i_1,i_2,\dots,i_H}^{(c)}.
\]
For our theoretical analysis we assume that $X$'s are independent from each other and so are $Z$'s. This assumption is simplistic, yet pervasively used in machine learning theory (plethora of decoupling strategies are discussed in~\cite{opac-b1095246}). Let $X$'s be identically distributed such that $X_{i_1,i_2,\dots,i_H}^{(c)}\sim\mathcal{N}(0,1)$. Therefore $Z_{i_1,i_2,\dots,i_H}\sim\mathcal{N}(0,1)$. Thus 
\begin{equation}
Y_{\Lambda}= q\!\!\!\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\sqrt{r_{i_1,i_2,\dots,i_H}}Z_{i_1,i_2,\dots,i_H}\rho\prod_{k = 1}^{H}w_{i_k}.
\label{eq:befapprox}
\end{equation}
Consider a family of networks which have the same graph of connections as network $\mathcal{N}$ but different edge weighting such that they only have $s$ unique weights and $s \leq \Lambda$. It was recently shown~\cite{NIPS2013_5025,DBLP:journals/corr/DentonZBLF14} that for large-size networks large number of network parameters (according to~\cite{NIPS2013_5025} even up to $95\%$) are reduntant and can either be learned from a very small set of unique parameters or even not learned at all with almost no loss in prediction accuracy.  In our experimental section we also demonstrate the empirical evidence of the overparametrization of neural networks. It is therefore well-justified to \textit{assume redunancy in network parametrization} where $s$ is the number of unique (non-redundant) parameters.

@@

Finally we assume that unique weights are close to being evenly distributed on the graph of connections of network $\mathcal{M}$. We call this assumption a \textit{uniformity assumption} (note it is analogous to the maximum entropy assumption). This assumption is in general consistent with the approach in~\cite{NIPS2013_5025}. To be more specific, this assumption implies that there exists some bounded non-negative constant $C$ such that for all $(i_1,i_2,\dots,i_H):i_1,i_2,\dots,i_H \in \{1,2,\dots,H\}$ and some $\delta \in [0,1]$ the following holds
\begin{equation}
(1-\delta)C\frac{\Psi}{\Lambda^H} \leq r_{i_1,i_2,\dots,i_H} \leq (1+\delta)C\frac{\Psi}{\Lambda^H},
\label{eq:uniform}
\end{equation}
where the factor $\frac{\Psi}{\Lambda^H}$ comes from the fact that for the network where every weight is uniformly distributed on the graph of connections (thus every node has equal probability of being adjacent to an edge with any of the unique weights) it holds that $r_{i_1,i_2,\dots,i_H} = \frac{\Psi}{\Lambda^H}$. Note that this condition can be sattified with small $\delta$ (close to $0$) if $s$ is sufficiently small.

Consider therefore an expression as follows
\begin{equation}
\hat{Y}_s = q\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}}Z_{i_1,i_2,\dots,i_H}\rho\prod_{k = 1}^{H}w_{i_k},
\label{eq:approx}
\end{equation}
which can be thought of as an output of some network $\mathcal{M}$ where the weights are still chosen from $\mathcal{A}$ but there are only $s$ unique weights in $\mathcal{A}$ among the total of $\Lambda$ weights, and furthermore every $H$ - length configuration of weights chosen from $\mathcal{A}$ is equally likely. Then the following theorem (Theorem~\ref{thm:unif}) captures the connection between $\hat{Y}_s$ and $Y_{\Lambda}$.

@@

Let $\mathcal{L}^a_{\Lambda,H}(w)$ and $\mathcal{L}^h_{\Lambda,H}(w)$ be the (random) absolute loss and (random) hinge loss defined as
\[\mathcal{L}^a_{\Lambda,H}({\bm w}) = |Y_t - \hat{Y}_s|
\]
and
\[\mathcal{L}^h_{\Lambda,H}({\bm w}) = \max(0,1-Y_t\hat{Y}_s).
\]
where $Y_t$ is a random variable corresponding the true data labeling that takes values $-1$ or $1$. Also note that in case of the hinge loss $\max$ operator can be modelled as Bernoulli random variable, that we will refer to as $M$, with success ($M = 1$) probability $\rho^{'}$. We assume $M$ is independent of $\hat{Y}_s$. Therefore we obtain that
\[\mathcal{L}^a_{N,H}({\bm w}) = \left \{
  \begin{tabular}{c}
  $\!\!\!\!\!\!1 - \hat{Y}_s$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = 1$ \\
  $\!1 + \hat{Y}_s$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = -1$ \\
  \end{tabular}
\right.
\]
and
\begin{eqnarray*}
\mathcal{L}^h_{\Lambda,H}({\bm w}) &=& \mathbb{E}_{M,A}[M(1-Y_t\hat{Y}_s)]\\&=& \left \{
  \begin{tabular}{c}
  $\!\!\!\!\!\!\mathbb{E}_{M}[M(1 - \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = 1$ \\
  $\!\mathbb{E}_{M}[M(1 + \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = -1$ \\
  \end{tabular}
\right.
\end{eqnarray*}
Note that both cases can be generalized to the following
\[\mathcal{L}_{\Lambda,H}({\bm w}) = \left \{
  \begin{tabular}{c}
  $\!\!\!\!\!\!\mathbb{E}_{M}[M(1 - \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = 1$ \\
  $\!\mathbb{E}_{M}[M(1 + \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = -1$ \\
  \end{tabular}
\right.,
\]
where in case of absolute loss $\rho^{'} = 1$. Furthermore, since $X$'s are Gaussian random variables, then so are $-X$'s thus we can further generalize that
\begin{eqnarray*}
\mathcal{L}_{\Lambda,H}({\bm w}) \!\!\!\!\!&=&\!\!\!\!\! \mathbb{E}_{M}[M(1 + \hat{Y}_s)]\\
&=& \!\!\!\!\!\rho^{'} + \rho^{'}\hat{Y}_s\\
&=& \!\!\!\!\!\rho^{'} + q\sqrt{\!\frac{\Psi}{\Lambda^H}\!}\!\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!Z_{i_1,i_2,\dots,i_H}\rho\rho^{'}\prod_{k = 1}^{H}w_{i_k}
\end{eqnarray*}
Let $\tilde{w}_i = \sqrt[H]{\rho\rho^{'}}w_i$ for all $i = \{1,2,\dots,k\}$.  Thus
\begin{equation}
\mathcal{L}_{\Lambda,H}({\bm w}) = \rho + q\sqrt{\frac{\Psi}{\Lambda^H}}\sum_{i_1,\dots,i_H=1}^{\Lambda}Z_{i_1,\dots,i_H}\prod_{k = 1}^{H}\tilde{w}_{i_k}.
\label{eq:befloss}
\end{equation}
We furthermore make a benign assumption that the weights sattisfy the spherical condition 
\begin{equation}
\frac{1}{\Lambda}\sum_{i=1}^{\Lambda}\tilde{w}_i^2 = 1
\label{eq:spherical}
\end{equation}
To simplify the notation in Equation~\ref{eq:befloss} we drop the letter accents and simply denote $\hat{w}$ as $w$. We skip constant $\rho$ as it does not matter when minimizing the loss function.
\begin{equation}
\mathcal{L}_{\Lambda,H}({\bm w}) = \frac{1}{\Lambda^{(H-1)/2}}\!\!\!\!\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!\!\!\!\!\!\!Z_{i_1,i_2,\dots,i_H}w_{i_1}w_{i_2}\dots\!w_{i_H},
\label{eq:spinglass}
\end{equation}
where the last inequality was obtained by substituting $q = \sqrt{\frac{\Lambda}{\Psi}}$. For the analysis $X$'s are assumed to be independent. Equation~\ref{eq:spinglass} is the centered Gaussian process on the sphere $\mathcal{S}_{N} = S^{N-1}(\sqrt{N})$ and is equivalent to the Hamiltonian of the $H$-spin spherical spin-glass model. The spherical constraint is captured in Equation~\ref{eq:spherical}. An asymptotic evaluation of the comlexity of spherical $H$-spin spherical spin-glass models via random matrix theory was studied in the literature~\cite{AAC2010} where a precise description of the energy landscape for the Hamiltonians of these models is provided. In this paper we explore a strong connection of the Hamiltonian of these models, originated from physics, and the strongly non-convex loss functions used in deep learning. We use the results of the theoretical analysis of the complexity of spin-glass models~\cite{AAC2010} to gain an understading of the optimization in deep learning.

@@

\section{Proof of Theorem~\ref{thm:redun}}
\begin{proof}
Note that $\mathbb{E}[\hat{Y}_s] = 0$ and $\mathbb{E}[Y_{\Lambda}] = 0$. Furthermore
\[\mathbb{E}[\hat{Y}_sY_{\Lambda}] = q^2\rho^2\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}r_{i_1,i_2,\dots,i_H}}\prod_{k = 1}^{H}w_{i_k}^2
\]
and
\[std(\hat{Y}_s) = q\rho\sqrt{\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\frac{\Psi}{\Lambda^H}\prod_{k = 1}^{H}w_{i_k}^2}
\]
\[std(Y_{\Lambda}) = q\rho\sqrt{\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}r_{i_1,i_2,\dots,i_H}\prod_{k = 1}^{H}w_{i_k}^2}.
\]
Therefore
\begin{eqnarray*}
&&\!\!\!\!\!\!\!\!\!corr(\hat{Y}_s,Y_{\Lambda})\\ 
&\!\!\!\!\!\!\!\!\!=&\!\!\!\!\!\!\! \frac{\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}r_{i_1,\dots,i_H}}\prod_{k = 1}^{H}w_{i_k}^2}{\sqrt{\!\!\!\left(\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\frac{\Psi}{\Lambda^H}\prod_{k = 1}^{H}w_{i_k}^2\right)\!\!\!\!\left(\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\!\!\!\!\!r_{i_1,\dots,i_H}\prod_{k = 1}^{H}w_{i_k}^2\right)}}\\
&\!\!\!\!\!\!\!\!\geq& \sqrt{\frac{1-\delta}{1+\delta}}, 
\end{eqnarray*}
where the last inequality is the direct consequence of the uniformity assumption of Equation~\ref{eq:uniform}.
\end{proof}

>>>>

\begin{definition}
The size of the network $\Lambda$ is the total number of network parameters: $\Lambda = \sum_{i=0}^{H-1}n_in_{i+1}$.
\end{definition}

@@

Let $\mathcal{W} = \{w_1,w_2,\dots,w_{\Lambda}\}$ be the set of all weights of the network. Furthermore let $\mathcal{A}_{\Lambda}$ denote the set of all $H$-length configuration of weights chosen from $\mathcal{W}$ (order of weights in a configuration does matter). Note that the size of $\mathcal{A}_{\Lambda}$ is therefore $\Lambda^H$. Also let $\mathcal{B}$ be a set such that each element correspond to the single configuration of weights from Equation~\ref{eq:befrein}, thus $\mathcal{B} = \{(w_{1,1}^1,w_{1,1}^2,\dots,w_{1,1}^H),(w_{1,2}^1,w_{1,2}^2,\dots,w_{1,2}^H),\dots,\\(w_{n_0,\gamma}^1,w_{n_0,\gamma}^2,\dots,w_{n_0,\gamma}^H)\}$, where every single weight comes from set $\mathcal{W}$. Note that in general there exist elements in $\mathcal{A}_{\Lambda}$ that will never appear in $\mathcal{B}$ (unless we allow repetition of weights in $\mathcal{W}$). Thus Equation~\ref{eq:befrein} can be equivalently written as 
\[Y \!=\! q\!\!\!\!\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!\!\!\left(r_{i_1,i_2,\dots,i_H}X_{i_1,i_2,\dots,i_H}A_{i_1,i_2,\dots,i_H}\right)\prod_{k = 1}^{H}w_{i_k},
\]
where $r_{i_1,i_2,\dots,i_H}$ denotes whether the configuration $(w_{i_1},w_{i_2},\dots,w_{i_H})$ appeared in Equation~\ref{eq:befrein} or not thus $r_{i_1,i_2,\dots,i_H} \in \{0\cup{1}\}$ and furthermore $\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}r_{i_1,i_2,\dots,i_H} = \Psi$. Assuming the independence of $X$'s and $A's$ we get
\begin{equation}
Y_{\Lambda} := \mathbb{E}_A[Y] = q\!\!\!\!\!\sum_{i_1,\dots,i_H=1}^{\Lambda}\!\!\!\!\!\!\!\left(r_{i_1,\dots,i_H}X_{i_1,\dots,i_H}\right)\rho\prod_{k = 1}^{H}\!\!w_{i_k}.
\label{eq:befapprox}
\end{equation}
For our theoretical analysis we also assume that $X$'s are independent identically distributed such that $X_{i_1,i_2,\dots,i_H}^{(c)}\sim\mathcal{N}(0,1)$. This assumption is simplistic, yet pervasively used in machine learning theory (plethora of decoupling strategies are discussed in~\cite{opac-b1095246}). Finally, let $Y_{\Lambda} = \mathbb{E}_A[Y]$, where in particular $\Lambda$ in this notation refers to the size of set $\mathcal{A}$ (this notation will be helpful later in this section).

Consider a family of networks which have the same graph of connections as network $\mathcal{N}$ but different edge weighting such that they only have $s$ unique weights and $s \leq \Lambda$. It was recently shown~\cite{NIPS2013_5025,DBLP:journals/corr/DentonZBLF14} that for large-size networks large number of network parameters (according to~\cite{NIPS2013_5025} even up to $95\%$) are reduntant and can either be learned from a very small set of unique parameters or even not learned at all with almost no loss in prediction accuracy.  In our experimental section we also demonstrate the empirical evidence of the overparametrization of neural networks. It is therefore well-justified to \textit{assume redunancy in network parametrization} where $s$ is the number of unique (non-redundant) parameters.

@@

Finally we assume that unique weights are close to being evenly distributed on the graph of connections of network $\mathcal{M}$. We call this assumption a \textit{uniformity assumption} (note it is analogous to the maximum entropy assumption). This assumption is in general consistent with the approach in~\cite{NIPS2013_5025}. To be more specific, this assumption implies that there exists some bounded non-negative constant $C$ such that for all $(i_1,i_2,\dots,i_H):i_1,i_2,\dots,i_H \in \{1,2,\dots,H\}$ and some $\delta \in [0,1]$ the following holds
\begin{equation}
(1-\delta)C\sqrt{\frac{\Psi}{\Lambda^H}} \leq r_{i_1,i_2,\dots,i_H} \leq (1+\delta)C\sqrt{\frac{\Psi}{\Lambda^H}},
\label{eq:uniform}
\end{equation}
where the factor $\sqrt{\frac{\Psi}{\Lambda^H}}$ comes from the fact that for the network where every weight is uniformly distributed on the graph of connections (thus every node has equal probability of being adjacent to an edge with any of the unique weights) it holds that $r_{i_1,i_2,\dots,i_H} = C\sqrt{\frac{\Psi}{\Lambda^H}}$. Note that this condition can be sattified with small $\delta$ (close to $0$) if $s$ is sufficiently small.

Consider therefore an expression as follows
\begin{equation}
\hat{Y}_s = Cq\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}}X_{i_1,i_2,\dots,i_H}\rho\prod_{k = 1}^{H}w_{i_k},
\label{eq:approx}
\end{equation}
which can be thought of as an output of some network $\mathcal{M}$ where the weights are still chosen from $\mathcal{A}$ but there are only $s$ unique weights in $\mathcal{A}$ among the total of $\Lambda$ weights, and furthermore every $H$ - length configuration of weights chosen from $\mathcal{A}$ is equally likely. Then the following theorem (Theorem~\ref{thm:unif}) captures the connection between $\hat{Y}_s$ and $Y_{\Lambda}$.

@@

Let $\mathcal{L}^a_{\Lambda,H}(w)$ and $\mathcal{L}^h_{\Lambda,H}(w)$ be the (random) absolute loss and (random) hinge loss defined as
\[\mathcal{L}^a_{\Lambda,H}({\bm w}) = |Y_t - \hat{Y}_s|
\]
and
\[\mathcal{L}^h_{\Lambda,H}({\bm w}) = \max(0,1-Y_t\hat{Y}_s).
\]
where $Y_t$ is a random variable corresponding the true data labeling that takes values $-1$ or $1$. Also note that in case of the hinge loss $\max$ operator can be modelled as Bernoulli random variable, that we will refer to as $M$, with success ($M = 1$) probability $\rho^{'}$. We assume $M$ is independent of $\hat{Y}_s$. Therefore we obtain that
\[\mathcal{L}^a_{N,H}({\bm w}) = \left \{
  \begin{tabular}{c}
  $\!\!\!\!\!\!1 - \hat{Y}_s$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = 1$ \\
  $\!1 + \hat{Y}_s$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = -1$ \\
  \end{tabular}
\right.
\]
and
\begin{eqnarray*}
\mathcal{L}^h_{\Lambda,H}({\bm w}) &=& \mathbb{E}_{M,A}[M(1-Y_t\hat{Y}_s)]\\&=& \left \{
  \begin{tabular}{c}
  $\!\!\!\!\!\!\mathbb{E}_{M}[M(1 - \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = 1$ \\
  $\!\mathbb{E}_{M}[M(1 + \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = -1$ \\
  \end{tabular}
\right.
\end{eqnarray*}
Note that both cases can be generalized to the following
\[\mathcal{L}_{\Lambda,H}({\bm w}) = \left \{
  \begin{tabular}{c}
  $\!\!\!\!\!\!\mathbb{E}_{M}[M(1 - \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = 1$ \\
  $\!\mathbb{E}_{M}[M(1 + \hat{Y}_s)]$ $\:\:\:\:$if$\:\:\:\:$ $Y_t = -1$ \\
  \end{tabular}
\right.,
\]
where in case of absolute loss $\rho^{'} = 1$. Furthermore, since $X$'s are Gaussian random variables, then so are $-X$'s thus we can further generalize that
\begin{eqnarray*}
\mathcal{L}_{\Lambda,H}({\bm w}) \!\!\!\!\!&=&\!\!\!\!\! \mathbb{E}_{M}[M(1 + \hat{Y}_s)]\\
&=& \!\!\!\!\!\rho^{'} + \rho^{'}\hat{Y}_s\\
&=& \!\!\!\!\!\rho^{'} + Cq\sqrt{\!\frac{\Psi}{\Lambda^H}\!}\!\!\!\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!\!\!\!\!Z_{i_1,i_2,\dots,i_H}\rho\rho^{'}\prod_{k = 1}^{H}w_{i_k}
\end{eqnarray*}
Let $\tilde{w}_i = \sqrt[H]{\rho\rho^{'}}w_i$ for all $i = \{1,2,\dots,k\}$.  Thus
\begin{equation}
\mathcal{L}_{\Lambda,H}({\bm w}) = \rho + Cq\sqrt{\frac{\Psi}{\Lambda^H}}\!\!\sum_{i_1,\dots,i_H=1}^{\Lambda}\!\!Z_{i_1,\dots,i_H}\prod_{k = 1}^{H}\tilde{w}_{i_k}.
\label{eq:befloss}
\end{equation}
We furthermore make a benign assumption that the weights sattisfy the spherical condition 
\begin{equation}
\frac{1}{\Lambda}\sum_{i=1}^{\Lambda}\tilde{w}_i^2 = 1
\label{eq:spherical}
\end{equation}
To simplify the notation in Equation~\ref{eq:befloss} we drop the letter accents and simply denote $\hat{w}$ as $w$. We skip constant $\rho$ as it does not matter when minimizing the loss function.
\begin{equation}
\mathcal{L}_{\Lambda,H}({\bm w}) = \frac{1}{\Lambda^{(H-1)/2}}\!\!\!\!\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!\!\!\!\!\!\!Z_{i_1,i_2,\dots,i_H}w_{i_1}w_{i_2}\dots\!w_{i_H},
\label{eq:spinglass}
\end{equation}
where the last inequality was obtained by substituting $q = \sqrt{\frac{\Lambda}{\Psi}}$ ans assuming, without loss of generality, that $C = 1$. For the analysis $X$'s are assumed to be independent. Equation~\ref{eq:spinglass} is the centered Gaussian process on the sphere $\mathcal{S}_{N} = S^{N-1}(\sqrt{N})$ and is equivalent to the Hamiltonian of the $H$-spin spherical spin-glass model. The spherical constraint is captured in Equation~\ref{eq:spherical}. An asymptotic evaluation of the comlexity of spherical $H$-spin spherical spin-glass models via random matrix theory was studied in the literature~\cite{AAC2010} where a precise description of the energy landscape for the Hamiltonians of these models is provided. In this paper we explore a strong connection of the Hamiltonian of these models, originated from physics, and the strongly non-convex loss functions used in deep learning. We use the results of the theoretical analysis of the complexity of spin-glass models~\cite{AAC2010} to gain an understading of the optimization in deep learning.

@@

\section{Proof of Theorem~\ref{thm:redun}}
\begin{proof}
Note that $\mathbb{E}[\hat{Y}_s] = 0$ and $\mathbb{E}[Y_{\Lambda}] = 0$. Furthermore
\[\mathbb{E}[\hat{Y}_sY_{\Lambda}] = C^2q^2\rho^2\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}r_{i_1,i_2,\dots,i_H}^2}\prod_{k = 1}^{H}w_{i_k}^2
\]
and
\[std(\hat{Y}_s) = Cq\rho\sqrt{\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\frac{\Psi}{\Lambda^H}\prod_{k = 1}^{H}w_{i_k}^2}
\]
\[std(Y_{\Lambda}) = Cq\rho\sqrt{\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}r_{i_1,i_2,\dots,i_H}^2\prod_{k = 1}^{H}w_{i_k}^2}.
\]
Therefore
\begin{eqnarray*}
&&\!\!\!\!\!\!\!\!\!corr(\hat{Y}_s,Y_{\Lambda})\\ 
&\!\!\!\!\!\!\!\!\!=&\!\!\!\!\!\!\! \frac{\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}r_{i_1,\dots,i_H}^2}\prod_{k = 1}^{H}w_{i_k}^2}{\sqrt{\!\!\!\left(\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\frac{\Psi}{\Lambda^H}\prod_{k = 1}^{H}w_{i_k}^2\right)\!\!\!\!\left(\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\!\!\!\!\!r_{i_1,\dots,i_H}^2\prod_{k = 1}^{H}w_{i_k}^2\right)}}\\
&\!\!\!\!\!\!\!\!\geq& \sqrt{\frac{1-\delta}{1+\delta}}, 
\end{eqnarray*}
where the last inequality is the direct consequence of the uniformity assumption of Equation~\ref{eq:uniform}.
\end{proof}
